Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
Minor

\begin{table}[t!] 
  \centering\scriptsize
  \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD, lower better). Our sparse \our ($M=256$) is on par with or better than full models (left) and outperforms the GP subset approach of \cite{todo}. See \cref{app:uci} for additional tables with comparisons.} 
	\label{tbl:uci}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{1pt}
	\setlength{\tblw}{0.08\textwidth}

@@

\subsection{Capturing uncertainty in UCI tasks under supervised learning}
\label{sec:uci}
%
We consider the same 8 UCI~\cite{UCI} classification benchamrks tasks and setup as were considered in \cite{todo}. We use a two-layer MLP for all tasks and follow the setup in \cref{sec:methods} for \our. After training, we construct the \our dual and use the resulting model for uncertainty quantification. We performed hyperparameter search over the prior precision $\delta$, and ran the experiment over $10$ seeds. %Depending on task dimension and complexity, our model can match the neural network MAP in negative log-predictive density (NLPD) even with a low number of inducing points (see \cref{tbl:uci} left).
In \cref{tbl:uci} (left), we compare our model to the NN MAP estimate, mean-field VI, a Baysian NN, and a GLM model (see \cite{add} for the baselines) in negative log-predictive density (NLPD). We match the predictive performance despite being sparse (here, $M=$). Results for $M=16,32,64,128,256$ included in \cref{app:uci} with full experiment details.

>>>>

\begin{table}[t!] 
  \centering\scriptsize
  \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD\textcolor{gray}{\footnotesize$\pm$std}, lower better). Our sparse \our ($M=256$) is on par with or better than full models (left) and outperforms the GP subset approach of \cite{todo}. See \cref{app:uci} for additional tables with comparisons.} 
	\label{tbl:uci}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{1pt}
	\setlength{\tblw}{0.08\textwidth}

@@

\subsection{Capturing uncertainty in UCI tasks under supervised learning}
\label{sec:uci}
%
We consider the same 8 UCI~\cite{UCI} classification benchamrks tasks and setup as were considered in \cite{todo}. We use a two-layer MLP for all tasks and follow the setup in \cref{sec:methods} for \our. After training, we construct the \our dual and use the resulting model for uncertainty quantification. We performed hyperparameter search over the prior precision $\delta$, and ran the experiment over 10 random splits. %Depending on task dimension and complexity, our model can match the neural network MAP in negative log-predictive density (NLPD) even with a low number of inducing points (see \cref{tbl:uci} left).
In \cref{tbl:uci} (left), we compare our model to the NN MAP estimate, mean-field VI, a Bayesian NN, and a GLM model (see \cite{add} for the baselines) in negative log-predictive density (NLPD). We match the predictive performance despite being sparse (here, $M=$). Results for $M=16,32,64,128,256$ included in \cref{app:uci} with full experiment details.
